### 2013-10-04 Rcode/test.mix.Rmd
added my_etruncnorm to improve numerical stability when [a,b] is far from the normal
added posterior mean and sd computations to mix.R

################################# TESTING #####################################
```{r}
source("mix.R")
temp = normalmix(c(0.5,0.5),c(-3,2),c(1,1))
x = seq(-5,5,length=100)
plot(x,dens(temp,x),type="l")
all.equal(compdens(temp,x),matdnorm(x, temp$mean,temp$sd))

@@

>>>>

################################# TESTING #####################################
```{r}
source("mix.R")
library("testthat")
temp = normalmix(c(0.5,0.5),c(-3,2),c(1,1))

expect_that(comp_mean(temp),equals(c(-3,2)))
expect_that(mixmean(temp),equals(-0.5))
expect_that(mixsd(temp),equals(2.692582))

x = seq(-5,5,length=100)
plot(x,dens(temp,x),type="l")
all.equal(compdens(temp,x),matdnorm(x, temp$mean,temp$sd))

@@

```{r}
etruncnorm(10,20,0,1)
my_etruncnorm(10,20,0,1)

etruncnorm(-20,-10,0,1)
my_etruncnorm(-20,-10,0,1)

etruncnorm(-20,-10,5,1)
my_etruncnorm(-20,-10,5,1)

etruncnorm(-30,-20,5,2)
my_etruncnorm(-30,-20,5,2)

etruncnorm(-Inf,-38,0,1)
my_etruncnorm(-Inf,-38,0,1)
